### 2020-03-11 papers.tex
Add reviews received thus far
Jenny's review exploit
Jenny's definitely blind review
Don't say we never did anything against you.
papers.tex: Assign three more of the reviews to specific submissions
papers.tex: "Title" the table of contents
Add papers 15 and 16

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{Academic Games}

@@

\addtrack
	{TODO}{THERE CAN BE ONLY ONE}
\addpaper
	{Anonymous paper}
	{Anonymous Author}
	{Keywords: anonymous, triple blind, review}
	{SIGBOVIK_2020_paper_1}
	{0cm}
	{}
\addpaper
	{A polynomial-time SAT algorithm}
	{Anonymous Author(s)}
	{Keywords: theoretical computer science, complexity theory, p versus np}
	{SIGBOVIK_2020_paper_2}
	{0cm}
	{}
\addpaper
	{Visualizing player engagement with virtual spaces using GIS}
	{Frederick Chan}
	{Keywords: geographic information systems, virtual spaces, video games, video game anthropology}
	{SIGBOVIK_2020_paper_3}
	{0cm}
	{}
\addpaper
	{Determining the laziest way to force other people to generate random numbers for us using IoT vulnerabilities}
	{mathmasterzach, StarChar}
	{Keywords: babies, information theory, randomness, entropy, April fools, hacking, the law, coffee shops, smart-toasters}
	{SIGBOVIK_2020_paper_4}
	{0cm}
	{}
\addpaper
	{A disproof of the Theorem of Triviality}
	{Arul Kolla, August Deer, Ethan Kogan}
	{Keywords: theorem of triviality, theorem, meta problems, meta, math i guess}
	{SIGBOVIK_2020_paper_5}
	{0cm}
	{}
\addpaper
	{Image2image neural network for addition and subtraction evaluation of a pair of not very large numbers}
	{Vladimir Ivashkin}
	{Keywords: neural network, computer vision, calculator}
	% TODO
	{../message-from-committee}
	{0cm}
	{}
\addpaper
	{Faking ancient computer science:\@ A special SIGBOVIK tutorial}
	{Roxanne van der Pol, Brian van der Bijl, Diederik M.\@ Roijers}
	{Keywords: ancient computer science, aliens, conspiracy theories, Triangle of Conspiracy Succession, probability, Arcaicam Esperantom, random number generator, pseudo-science}
	{SIGBOVIK_2020_paper_7}
	{0cm}
	{}
\addpaper
	{Making explicit a constant appearing in an impossible equation of Carl and Moroz}
	{Matthew Weidner}
	{Keywords: computational mathematics, Hilbert's tenth problem, Diophantine sets}
	{SIGBOVIK_2020_paper_8}
	{0cm}
	{}
\addpaper
	{Can a paper be written entirely in the title? 1. Introduction: The title pretty much says it all. 2. Evaluation: It gets the job done. However, the title is a little long. 3. Conclusion: Yes.}
	{Daniel Gaston}
	{Keywords: innovation, strength, progress}
	{SIGBOVIK_2020_paper_9}
	{0cm}
	{}
\addpaper
	{RegisToken}
	{Irene Lin, Arnaud Avondet, Preston Vander Vos}
	{Keywords: blockchain, Ethereum, token, FCE, course registration}
	{SIGBOVIK_2020_paper_10}
	{0cm}
	{}
\addpaper
	{Erd\"os-Bacon-Sabbath numbers: \textit{Reductio ad absurdum}}
	{Maria Klawe \textit{et al.}\@ (incl.\@ Harry Q.\@ Bovik!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!1)}
	{Keywords: Paul Erd\"os, Kevin Bacon, Black Sabbath}
	% TODO
	{../message-from-committee}
	{0cm}
	{}
\addpaper
	{Formulating the syntactically simplest programming language}
	{Brendon Boldt}
	{Keywords: proramming languages, compilers, formal grammars}
	{SIGBOVIK_2020_paper_12}
	{0cm}
	{}
\addpaper
	{Training ImageNet in 1 second: Early stopping theoretical accelerate training}
	{Yiping Lu, Denny Wu}
	{Keywords: optimization, deep learning, machine learning theory}
	% TODO
	{../message-from-committee}
	{0cm}
	{}
\addpaper
	{Artificial general relativity}
	{Pablo Samuel Castro}
	{Keywords: physics, artificial, general relativity, quantum physics, universe-changing, new science, field equations, black holes}
	{SIGBOVIK_2020_paper_14}
	{0cm}
	{}

>>>>

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{TODO: Craft a clever but cumbersome heading}

@@

\addtrack
	{TODO}{THERE CAN BE ONLY ONE}
\addpaper
	{Anonymous paper}
	{Anonymous Author}
	{Keywords: anonymous, triple blind, review}
	{SIGBOVIK_2020_paper_1}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_7}{0cm}
\addpaper
	{A polynomial-time SAT algorithm}
	{Anonymous Author(s)}
	{Keywords: theoretical computer science, complexity theory, p versus np}
	{SIGBOVIK_2020_paper_2}
	{0cm}
	{}
\addpaper
	{Visualizing player engagement with virtual spaces using GIS}
	{Frederick Chan}
	{Keywords: geographic information systems, virtual spaces, video games, video game anthropology}
	{SIGBOVIK_2020_paper_3}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_2}{0cm}
\addpaper
	{Determining the laziest way to force other people to generate random numbers for us using IoT vulnerabilities}
	{mathmasterzach, StarChar}
	{Keywords: babies, information theory, randomness, entropy, April fools, hacking, the law, coffee shops, smart-toasters}
	{SIGBOVIK_2020_paper_4}
	{0cm}
	{}
\addpaper
	{A disproof of the Theorem of Triviality}
	{Arul Kolla, August Deer, Ethan Kogan}
	{Keywords: theorem of triviality, theorem, meta problems, meta, math i guess}
	{SIGBOVIK_2020_paper_5}
	{0cm}
	{}
\addpaper
	{Image2image neural network for addition and subtraction evaluation of a pair of not very large numbers}
	{Vladimir Ivashkin}
	{Keywords: neural network, computer vision, calculator}
	% TODO
	{../message-from-committee}
	{0cm}
	{}
\addpaper
	{Faking ancient computer science:\@ A special SIGBOVIK tutorial}
	{Roxanne van der Pol, Brian van der Bijl, Diederik M.\@ Roijers}
	{Keywords: ancient computer science, aliens, conspiracy theories, Triangle of Conspiracy Succession, probability, Arcaicam Esperantom, random number generator, pseudo-science}
	{SIGBOVIK_2020_paper_7}
	{0cm}
	{}
\addpaper
	{Making explicit a constant appearing in an impossible equation of Carl and Moroz}
	{Matthew Weidner}
	{Keywords: computational mathematics, Hilbert's tenth problem, Diophantine sets}
	{SIGBOVIK_2020_paper_8}
	{0cm}
	{}
\addpaper
	{Can a paper be written entirely in the title? 1. Introduction: The title pretty much says it all. 2. Evaluation: It gets the job done. However, the title is a little long. 3. Conclusion: Yes.}
	{Daniel Gaston}
	{Keywords: innovation, strength, progress}
	{SIGBOVIK_2020_paper_9}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_1}{0cm}
\addpaper
	{RegisToken}
	{Irene Lin, Arnaud Avondet, Preston Vander Vos}
	{Keywords: blockchain, Ethereum, token, FCE, course registration}
	{SIGBOVIK_2020_paper_10}
	{0cm}
	{}
\addpaper
	{Erd\"os-Bacon-Sabbath numbers: \textit{Reductio ad absurdum}}
	{Maria Klawe \textit{et al.}\@ (incl.\@ Harry Q.\@ Bovik!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!1)}
	{Keywords: Paul Erd\"os, Kevin Bacon, Black Sabbath}
	% TODO
	{../message-from-committee}
	{0cm}
	{}
\addpaper
	{Formulating the syntactically simplest programming language}
	{Brendon Boldt}
	{Keywords: proramming languages, compilers, formal grammars}
	{SIGBOVIK_2020_paper_12}
	{0cm}
	{}
\addpaper
	{Training ImageNet in 1 second: Early stopping theoretical accelerate training}
	{Yiping Lu, Denny Wu}
	{Keywords: optimization, deep learning, machine learning theory}
	% TODO
	{../message-from-committee}
	{0cm}
	{}
\addpaper
	{Artificial general relativity}
	{Pablo Samuel Castro}
	{Keywords: physics, artificial, general relativity, quantum physics, universe-changing, new science, field equations, black holes}
	{SIGBOVIK_2020_paper_14}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_5}{0cm}
\addpaper
	{Synthesizing programs by asking people for help online}
	{Cassie Jones}
	{Keywords: program synthesis, cloud computing, social computation, the real program synthesizer was the friends we made along the way}
	{SIGBOVIK_2020_paper_15}
	{0cm}
	{}
\addpaper
	{Empire Machines and beyond}
	{Dar\'io de la Fuente Garc\'ia, F\'elix \'Axel Gimeno Gil, Juan Carlos Morales Vega}
	{Keywords: finite-state machines, models of computation, Empire Machines, doing research like this is awesome, Civilization XXIV (when it comes out)}
	{SIGBOVIK_2020_paper_16}
	{0cm}
	{}

% TODO
\addreview{SIGBOVIK_2020_review_3}{0cm}
\addreview{SIGBOVIK_2020_review_4}{0cm}
\addreview{SIGBOVIK_2020_review_6}{0cm}
